Автоматическая регуляризации байесовских нейронных сетей

### 2025-01-12 article/article.tex
Опечатки

    Подставив (\ref{sigma_def}) и (\ref{mu_def}) в (\ref{kl_init}) и (\ref{elbo_kl}), получим:
    \begin{equation}\label{kl_optim_rho_gamma}
        KL(q_{\pmb{\theta}}(\pmb{W})~||~p(\pmb{W}))
        =
            \frac{1}{2} \sum_{k=1}^{M} \ln(
                {1 + \gamma_{k}^{2}}
            )
    \end{equation}
    \begin{equation}\label{elbo_kl_optim_rho_gamma}
        \mathcal{L}
        \approx
            \frac{1}{S} \sum_{j=1}^S \sum_{i=1}^{L} {
                \ln{
                    p(\pmb{y_{i}} | \pmb{x_{i}}, \pmb{\hat{W}_{ij}})
                }
            }
        -
            \frac{1}{2} \sum_{k=1}^{M} \ln(
                {1 + \gamma_{k}^{2}}
            )
    \end{equation}

@@

\begin{thebibliography}{0}
    \bibitem{mackay_1992a}
        MacKay, D. J. C. (1992a).
        Bayesian interpolation. Neural Computation 4(3), 415–447.
    \bibitem{mackay_1992b}
        MacKay, D. J. C. (1992b).
        The evidence framework applied to classification networks.
        Neural Computation 4(5), 720–736.
    \bibitem{mackay_1992c}
        MacKay, D. J. C. (1992c).
        A practical Bayesian framework for back-propagation networks.
        Neural Computation 4(3), 448–472.
    \bibitem{mackay_1994}
        MacKay, D. J. C. (1994).
        Bayesian methods for backprop networks.
        In E. Domany, J. L. van Hemmen, and K. Schulten (Eds.),
        Models of Neural Networks, III, Chapter 6, pp. 211–254.
        Springer.
    \bibitem{mackay_1995}
        MacKay, D. J. C. (1995).
        Probable networks and plausible predictions~---
        a review of practical Bayesian methods for supervised neural networks”.
        In: Network: Computation in Neural Systems 6.3, pp. 469–505.
    \bibitem{nea_96}
        R. Neal. (1996).
        Bayesian learning for neural networks.
        Springer.
    \bibitem{tipping_01}
        Tipping, M. E. (2001).
        Sparse Bayesian learning and the relevance vector machine.
        Journal of Machine Learning Research 1, 211–244.
    \bibitem{hinton_van_camp_1993}
        Hinton, G. E. and D. van Camp (1993).
        Keeping neural networks simple by minimizing the description length of the weights.
        In Proceedings of the Sixth Annual Conference on Computational Learning Theory, pp. 5–13. ACM.
    \bibitem{gra_11}
        A. Graves (2011).
        Practical Variational Inference for Neural Networks.
        NIPS.
    \bibitem{blu_15}
        C. Blundell, J. Cornebise, K. Kavukcuoglu, and D. Wierstra. (2015).
        Weight Uncertainty in Neural Networks.
        ICML.
    \bibitem{kingma_2013}
        Kingma D. P., Welling M. (2013).
        Welling M. Auto-Encoding Variational Bayes. ArXiv e-prints.
    \bibitem{nal_18}
        E. T. Nalisnick. (2018).
        On Priors for Bayesian Neural Networks.
        PhD thesis. UC Irvine.
    \bibitem{wi_20}
        A. G. Wilson and P. Izmailov. (2020).
        Bayesian Deep Learning and a Probabilistic Perspective of Generalization.
        NIPS.
    \bibitem{hoe_21}
        T. Hoefler, D. Alistarh, T. Ben-Nun, N. Dryden, and A. Peste. (2021).
        “Sparsity in Deep Learning:
        Pruning and growth for efficient inference and training in neural networks.
        In arXiv: 2102.00554.
    \bibitem{for_22}
        V. Fortuin. (2022).
        Priors in Bayesian Deep Learning: A Review.
        In: Intl. Statisical Review.
    \bibitem{bishop2006}
        C. Bishop (2006).
        Pattern recognition and machine learning.
        Springer.
    \bibitem{murphy_book_1}
        Kevin P. Murphy. (2022).
        Probabilistic Machine Learning: An introduction.
        MIT Press.
    \bibitem{murphy_book_2}
        Kevin P. Murphy. (2023).
        Probabilistic Machine Learning: Advanced Topics.
        MIT Press.
\end{thebibliography}

>>>>

    Подставив (\ref{sigma_def}) и (\ref{mu_def}) в (\ref{kl_optim}) и (\ref{elbo_kl_optim}), получим:
    \begin{equation}\label{kl_optim_rho_gamma}
        KL(q_{\pmb{\theta}}(\pmb{W})~||~p(\pmb{W}))
        =
            \frac{1}{2} \sum_{k=1}^{M} \ln(
                {1 + \gamma_{k}^{2}}
            )
    \end{equation}
    \begin{equation}\label{elbo_kl_optim_rho_gamma}
        \mathcal{L}
        \approx
            \frac{1}{S} \sum_{j=1}^S \sum_{i=1}^{L} {
                \ln{
                    p(\pmb{y_{i}} | \pmb{x_{i}}, \pmb{\hat{W}_{ij}})
                }
            }
        -
            \frac{1}{2} \sum_{k=1}^{M} \ln(
                {1 + \gamma_{k}^{2}}
            )
    \end{equation}

@@

\begin{thebibliography}{0}
    \bibitem{mackay_1992a}
        MacKay, D. J. C. (1992a).
        Bayesian interpolation. Neural Computation 4(3), 415–447.
    \bibitem{mackay_1992b}
        MacKay, D. J. C. (1992b).
        The evidence framework applied to classification networks.
        Neural Computation 4(5), 720–736.
    \bibitem{mackay_1992c}
        MacKay, D. J. C. (1992c).
        A practical Bayesian framework for back-propagation networks.
        Neural Computation 4(3), 448–472.
    \bibitem{mackay_1994}
        MacKay, D. J. C. (1994).
        Bayesian methods for backprop networks.
        In E. Domany, J. L. van Hemmen, and K. Schulten (Eds.),
        Models of Neural Networks, III, Chapter 6, pp. 211–254.
        Springer.
    \bibitem{mackay_1995}
        MacKay, D. J. C. (1995).
        Probable networks and plausible predictions~---
        a review of practical Bayesian methods for supervised neural networks”.
        In: Network: Computation in Neural Systems 6.3, pp. 469–505.
    \bibitem{nea_96}
        R. Neal. (1996).
        Bayesian learning for neural networks.
        Springer.
    \bibitem{tipping_01}
        Tipping, M. E. (2001).
        Sparse Bayesian learning and the relevance vector machine.
        Journal of Machine Learning Research 1, 211–244.
    \bibitem{hinton_van_camp_1993}
        Hinton, G. E. and D. van Camp (1993).
        Keeping neural networks simple by minimizing the description length of the weights.
        In Proceedings of the Sixth Annual Conference on Computational Learning Theory, pp. 5–13. ACM.
    \bibitem{gra_11}
        A. Graves (2011).
        Practical Variational Inference for Neural Networks.
        NIPS.
    \bibitem{blu_15}
        C. Blundell, J. Cornebise, K. Kavukcuoglu, and D. Wierstra. (2015).
        Weight Uncertainty in Neural Networks.
        ICML.
    \bibitem{kingma_2013}
        Kingma D. P., Welling M. (2013).
        Welling M. Auto-Encoding Variational Bayes. ArXiv e-prints.
    \bibitem{nal_18}
        E. T. Nalisnick. (2018).
        On Priors for Bayesian Neural Networks.
        PhD thesis. UC Irvine.
    \bibitem{wi_20}
        A. G. Wilson and P. Izmailov. (2020).
        Bayesian Deep Learning and a Probabilistic Perspective of Generalization.
        NIPS.
    \bibitem{hoe_21}
        T. Hoefler, D. Alistarh, T. Ben-Nun, N. Dryden, and A. Peste. (2021).
        Sparsity in Deep Learning:
        Pruning and growth for efficient inference and training in neural networks.
        In arXiv: 2102.00554.
    \bibitem{for_22}
        V. Fortuin. (2022).
        Priors in Bayesian Deep Learning: A Review.
        In: Intl. Statisical Review.
    \bibitem{bishop2006}
        C. Bishop (2006).
        Pattern recognition and machine learning.
        Springer.
    \bibitem{murphy_book_1}
        Kevin P. Murphy. (2022).
        Probabilistic Machine Learning: An introduction.
        MIT Press.
    \bibitem{murphy_book_2}
        Kevin P. Murphy. (2023).
        Probabilistic Machine Learning: Advanced Topics.
        MIT Press.
\end{thebibliography}
